Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.

### 2021-01-27 RR_manuscript/Draft_RR.tex
:memo: - render RR + bib updates

Data analysis comes with many decisions like how to measure a given phenomenon or behavior, what data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision procedure to apply.
However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes.
This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
Humans filter the world in irrational ways (e.g., Tversky \& Kahneman, 1974), seeing coherent patterns in randomness (Brugger 2001), convincing themselves of the validity of prior expectations ({``I knew it,''} Nickerson, 1998), and perceiving events as being plausible in hindsight ({``I knew it all along,''} Fischhoff, 1975).
In connection with an academic incentive system that rewards certain discovery processes more than others (Koole \& Lakens, 2012; Sterling, 1959), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways to measure (Roettger, 2019).
Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions.
Consequently, there might be many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies (Gelman \& Loken, 2014; e.g., Simmons, Nelson, \& Simonsohn, 2011).
These interpretations are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analyzed differently.
However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical re-analyses of published analytic strategies are still not very common because data sharing remains rare (Wicherts, Borsboom, Kats, \& Molenaar, 2006).

@@

Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances (e.g., Ladd, 2008).
Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g.~Niebuhr et al., 2011).
The latter can also be expressed by global vs local pitch modulations (Haan 2002), as well as acoustic information within the temporal or spectral domain (e.g., Van Heuven \& Van Zanten, 2005).
Extra-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch (Foulkes \& Docherty, 2006; Ogden, 2004; White, Payne, \& Mattys, 2009).

@@

(2a) ``I can't bear ANOTHER meeting on zoom.''\\
(2b) ``I can't bear another meeting on ZOOM.''

@@

\begin{figure}
\includegraphics[width=1\linewidth]{/Users/ste/repos/many_analyses/figs/ForkingPaths} \caption{Illustrations of the analytical flexibility associated with acoustic analyses. (A) an example of multiple possible and justifiable decisions when comparing to utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b. The words ``another is highlighted by the green box'\,'; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch.}\label{fig:forkingPaths}
\end{figure}

@@

These decisions are usually made prior to any statistical analysis, but are at times revised a posteriori (i.e.~after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis (e.g.~Wicherts et al.~????).
Even the analysis of a single measure can be approached via an ever-increasing range of different statistical models (REFs).
The present paper probes this garden of forking paths in the analysis of speech.
To assess the variability in data analysis pipelines across independent researchers, we provided XX analytical teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.

@@

To identify the minimal sample size, we followed the method in {[}ECO RR{]}.
The aim of the meta-analysis is to obtain an estimate of heterogeneity of the effect sizes reported by the analysis teams (\(\tau^2\), i.e.~the variance \(\sigma^2_{\alpha_{\text{team}}}\), see \Cref{s:meta-est}).
Ideally, the 95\% credible interval (CrI) of \(\tau^2\) should not include 0 (i.e.~the probability \(p\) that the 95\% CrI contains 0 should be less than 0.05).
The probability \(p\) that a CrI interval does not include 0 is obtained via the \emph{t}-statistics:

@@

To summarize the variability in reported effect sized, we will follow Bayesian random-effects meta-analytical techniques.
Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/random-effects regression models, so that common effect size measures such as Cohen's \(d\) would be inappropriate.
Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hz for frequency vs ms for duration), we will standardize all reported effects by refitting each reported model with centered and scaled continuous variables (\emph{z}-scores, i.e.~the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
\highlight[id=SC, comment = {Is this sentence good?}]{Factor-level ordering} for each factor variable will be decided on a model-by-model basis, depending on which levels were compared by the team.
Each standardized (refitted) model will be fitted as a Bayesian regression model with Stan (\textbf{stan-development-team2020?}), RStan (\textbf{stan-development-team2020a?}), and brms (\textbf{burkner2017?}) in R (\textbf{r-core-team2020?}).
For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), making the standardized models in fact equivalent to the reported frequentist models.
If a team has fitted Bayesian models, the same priors as reported by the team will be used in fitting the respective standardized model.

@@

\[
\begin{aligned}
\eta_i      & \sim \text{Normal}(\mu_i, \sigma_i) \\
\mu_i       & = \alpha + \alpha_{\text{team}[i]} \\
\alpha      & \sim \text{Normal}(0, 1) \\
\sigma_{\alpha_{\text{team}}} & \sim \text{HalfCauchy}(0, 1) \\
\sigma_i    & = \text{se}_i
\end{aligned}
\]

The outcome variable will be the set of standardized effect sizes \(\eta_i\).
The likelihood of \(\eta_i\) is assumed to correspond to a normal distribution (Knight, 2000).
The analysis teams will constitute the group-level effect (i.e., random effect, \texttt{(1\ \textbar{}\ team)}).
The standard errors \(\text{se}_i\) will be included as the standard deviation \(\sigma_i\) of \(\eta_i\) to fit a measurement-error model, as discussed above.
We will use regularizing weakly-informative priors for the intercept \(\alpha\) (\(Normal(0, 1)\)) and for the group-level standard deviation \(\alpha_{\text{team}[i]}\) (\(HalfCauchy(0, 1)\)).
We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan, and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
\highlight[id=SC, comment = {This ok?}]{In case of issues from divergent transitions} in the sampling, we will increase \texttt{adapt\_delta}, \texttt{tree\_depth}, and the number of iterations in this order until there are no divergent transitions.
The analysis will be conducted in R (\textbf{r-core-team2020?}) and fit using Stan (\textbf{stan-development-team2020?}), RStan (\textbf{stan-development-team2020a?}), and brms (\textbf{burkner2017?}).
The code used to run the model can be found here: INSERT LINK.

The posterior probability of the population-level intercept \(\alpha\) will give us an estimate of the range of probable values of the standardized effect size \(\hat{\eta}\).
This posterior probability will also form the basis \highlight[id=SC, comment = {A lot of "of"s...}]{of} the investigation of the effect of a set of analytical and demographic factors, detailed in Section \ref{ana-factors}.
Crucially, the posterior probability of \(\sigma_{\alpha_{\text{team}}}\) (the standard deviation of the the group-level effect of team) will allow us to quantify the degree of variation between teams on a standardized scale.

@@

As a second step, we will investigate the extent to which deviations from the meta-analytical mean by individual standardized effect sizes relate to a series of predictors related to analytical and demographic factors (see below).
The deviation score \(\delta_i\), which serves as the dependent variable in this analysis, will be the \highlight[id=SC, comment = {We might wanna fit a me model. See minutes.}]{difference between the meta-analytical mean} (\(\hat{\eta}\)) and the individual standardized effect size of each analysis (\(\eta_i\)).
We will fit a single Bayesian regression model with \(\delta_i\) as the outcome variable, and the analytical and demographic factors described in the following paragraphs as predictors.

@@

\begin{itemize}
\tightlist
\item
  \emph{Measure of uniqueness} of individual analyses for the set of predictors in each model.
\item
  \emph{Measure of conservativeness} of the model specification.
\item
  \emph{Number of post-hoc changes to the acoustic measurements} the teams will report to have carried out.
\item
  \emph{Number of models} the teams will report to have run.
\item
  \emph{Major dimension} that has been measured to answer the research question.
\item
  \emph{Temporal window} that the measurement is taken over.
\item
  \emph{Data exclusion}, whether data has been excluded or not.
\end{itemize}

The measure of uniqueness of predictors will be assessed by the Sørensen-Dice Index (SDI, Dice, 1945; Sørensen, 1948).
The SDI is an index typically used in ecology research to compare species composition across sites.
For our purposes, we will treat predictors as species and individual analyses as sites.
The SDI for a pair of analyses \((X, Y)\) can be obtained using the following formula:

@@

where \(|X \cap Y|\) is the number of variables common to both models, and \(|X|+|Y|\) is the sum of the number of variables that occur in each model.

In order to generate a unique SDI for each analysis team, we will calculate the average of all pairwise SDIs for all pairs of analyses using the \texttt{beta.pair()} function in the betapart R package (Baselga et al.~2018).

The major measurement dimension of each analysis will be categorized according to the following possible groups: duration, amplitude, fundamental frequency, other spectral properties (e.g.~frequency center of gravity, harmonics difference, etc.), other measures (e.g.~principal components, vowel dispersion, etc.)
The temporal window that the measurement is taken over is defined by the target linguistic unit.
We assume the following relevant linguistic units: segment, syllable, word, phrase.

\textbf{Demographic factors}. We will include the following demographic factors about the \highlight[id=SC, comment = {How do we do this, since we will have a score per individual rather than per team?}]{analysis} teams:

\begin{itemize}
\tightlist
\item
  \emph{Research experience} as the elapsed time from PhD award (negative values will indicate that the person is a student or graduate student).
\item
  \emph{Initial belief} in the presence of an effect of atypical noun-adjective pairs on acoustics, as answered during the intake questionnaire.
\end{itemize}

@@

@@

@@

@@

@@

>>>>

Data analysis comes with many decisions like how to measure a given phenomenon or behavior, what data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision procedure to apply.
However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes.
This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
Humans filter the world in irrational ways (e.g., Tversky \& Kahneman, 1974), seeing coherent patterns in randomness (Brugger, 2001), convincing themselves of the validity of prior expectations ({``I knew it,''} Nickerson, 1998), and perceiving events as being plausible in hindsight ({``I knew it all along,''} Fischhoff, 1975).
In connection with an academic incentive system that rewards certain discovery processes more than others (Koole \& Lakens, 2012; Sterling, 1959), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways to measure (Roettger, 2019).
Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions.
Consequently, there might be many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies (Gelman \& Loken, 2014; e.g., Simmons, Nelson, \& Simonsohn, 2011).
These interpretations are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analyzed differently.
However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical re-analyses of published analytic strategies are still not very common because data sharing remains rare (Wicherts, Borsboom, Kats, \& Molenaar, 2006).

@@

Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances (e.g., Ladd, 2008).
Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g.~Niebuhr et al., 2011).
The latter can also be expressed by global vs local pitch modulations (Van Heuven, Haan, Gussenhoven, \& Warner, 2002), as well as acoustic information within the temporal or spectral domain (e.g., Van Heuven \& Van Zanten, 2005).
Extra-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch (Foulkes \& Docherty, 2006; Ogden, 2004; White, Payne, \& Mattys, 2009).

@@

(2a) ``I can't bear ANOTHER meeting on zoom.''
(2b) ``I can't bear another meeting on ZOOM.''

@@

\begin{figure}
\includegraphics[width=1\linewidth]{/Users/ste/repos/many_analyses/figs/ForkingPaths} \caption{Illustrations of the analytical flexibility associated with acoustic analyses. (A) an example of multiple possible and justifiable decisions when comparing to utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b. The words ``another is highlighted by the green box''; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch.}\label{fig:forkingPaths}
\end{figure}

@@

These decisions are usually made prior to any statistical analysis, but are at times revised a posteriori (i.e.~after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis {[}e.g.~wicherts2016{]}.
Even the analysis of a single measure can be approached via an ever-increasing range of different statistical models (REFs).
The present paper probes this garden of forking paths in the analysis of speech.
To assess the variability in data analysis pipelines across independent researchers, we provided XX analytical teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.

@@

To identify the minimal sample size, we followed the method in {[}ECO RR{]}.
The aim of the meta-analysis is to obtain an estimate of heterogeneity of the effect sizes reported by the analysis teams (\(\tau^2\), i.e.~the variance \(\sigma^2_{\alpha_{\text{t}}}\), see \Cref{s:meta-est}).
Ideally, the 95\% credible interval (CrI) of \(\tau^2\) should not include 0 (i.e.~the probability \(p\) that the 95\% CrI contains 0 should be less than 0.05).
The probability \(p\) that a CrI interval does not include 0 is obtained via the \emph{t}-statistics:

@@

To summarize the variability in reported effect sized, we will follow Bayesian random-effects meta-analytical techniques.
Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/random-effects regression models, so that common effect size measures such as Cohen's \(d\) would be inappropriate.
Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hz for frequency vs ms for duration), we will standardize all reported effects by refitting each reported model with centered and scaled continuous variables (\emph{z}-scores, i.e.~the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
\highlight[id=SC, comment = {Is this sentence good?}]{Factor-level ordering} for each factor variable will be decided on a model-by-model basis, depending on which levels were compared by the team.
Each standardized (refitted) model will be fitted as a Bayesian regression model with Stan (Stan Development Team, 2021), RStan (Stan Development Team, 2020), and brms (Bürkner, 2017) in R (R Core Team, 2020).
For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), making the standardized models in fact equivalent to the reported frequentist models.
If a team has fitted Bayesian models, the same priors as reported by the team will be used in fitting the respective standardized model.

@@

\[
\begin{aligned}
\eta_i      & \sim \text{Normal}(\mu_i, \sigma_i) \\
\mu_i       & = \alpha + \alpha_{\text{t}[i]} \\
\alpha      & \sim \text{Normal}(0, 1) \\
\sigma_{\alpha_{\text{t}}} & \sim \text{HalfCauchy}(0, 1) \\
\sigma_i    & = \text{se}_i
\end{aligned}
\]

The outcome variable will be the set of standardized effect sizes \(\eta_i\).
The likelihood of \(\eta_i\) is assumed to correspond to a normal distribution (Knight, 2000).
The analysis teams will constitute the group-level effect (i.e., random effect, \texttt{(1\ \textbar{}\ team)}).
The standard errors \(\text{se}_i\) will be included as the standard deviation \(\sigma_i\) of \(\eta_i\) to fit a measurement-error model, as discussed above.
We will use regularizing weakly-informative priors for the intercept \(\alpha\) (\(Normal(0, 1)\)) and for the group-level standard deviation \(\alpha_{\text{t}[i]}\) (\(HalfCauchy(0, 1)\)).
We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan, and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
\highlight[id=SC, comment = {This ok?}]{In case of issues from divergent transitions} in the sampling, we will increase \texttt{adapt\_delta}, \texttt{tree\_depth}, and the number of iterations in this order until there are no divergent transitions.
The analysis will be conducted in R (R Core Team, 2020) and fit using Stan (Stan Development Team, 2021), RStan (Stan Development Team, 2020), and brms (Bürkner, 2017).
The code used to run the model can be found here: INSERT LINK.

The posterior probability of the population-level intercept \(\alpha\) will give us an estimate of the range of probable values of the standardized effect size \(\hat{\eta}\).
This posterior probability will also form the basis \highlight[id=SC, comment = {A lot of "of"s...}]{of} the investigation of the effect of a set of analytical and demographic factors, detailed in Section \ref{ana-factors}.
Crucially, the posterior probability of \(\sigma_{\alpha_{\text{t}}}\) (the standard deviation of the the group-level effect of team) will allow us to quantify the degree of variation between teams on a standardized scale.

@@

As a second step, we will investigate the extent to which deviations from the meta-analytical mean by individual standardized effect sizes relate to a series of predictors related to analytical and demographic factors (see below).
We will fit a single Bayesian regression model with each team's group-level coefficient \(\alpha_{\text{t}[i]}\) as the outcome variable, and the analytical and demographic factors described below as predictors.
The coefficient \(\alpha_{\text{t}[i]}\) can be interpreted as the deviation score of the team's \(\eta_i\) from the meta-analytical mean, allowing us to determine potential effects of analytical and demographic factors on how the teams deviate from the meta-analytical mean.
Since each \(\alpha_{\text{t}[i]}\) comes with uncertainty, quantified by its standard deviation \(\sigma_{\alpha_{\text{t}[i]}}\), we will fit a measurement-error model, as we did in the meta-analytical model above.
The formula of the model is the following (see the description of the predictors below for the meaning of acronyms):

\[
\begin{aligned}
\alpha_{\text{t}[i]}      & \sim \text{Normal}(\mu_{\alpha_{t[i]}}, \sigma_i) \\
\mu_{\alpha_{t[i]}}       & = \iota + \upsilon_u\cdot uniq_i + \upsilon_c\cdot cons_i + \upsilon_p\cdot phoc_i + \upsilon_m\cdot modn_i + \upsilon_d\cdot mdim_i + \upsilon_w\cdot twin_i + \upsilon_e\cdot excl_i \\
 & \qquad\qquad +\upsilon_{xp}\cdot rexp_i + \upsilon_{be}\cdot belf_i  \\
\iota      & \sim \text{Normal}(0, 1) \\
\upsilon_{[\ldots]} & \sim \text{Normal}(0,1) \\
resp_i & \sim \text{Normal}(\mu_{resp_i}, \sigma_{resp_i}) \\
belf_i & \sim \text{Normal}(\mu_{belf_i}, \sigma_{belf_i}) \\
\sigma_i    & = \sigma_{\alpha_{t[i]}}
\end{aligned}
\]

The likelihood of \(\alpha_{t[i]}\) is a normal distribution.
The mean is based on the overall intercept \(i\) and on the \(\upsilon\) coefficient of each predictor.
The numeric predictors will be centered and scaled and the categorical predictors will be sum coded.
As the prior for \(i\) and \(\upsilon\) we will use a normal distribution with mean 0 and standard deviation 1.

@@

\begin{itemize}
\tightlist
\item
  \emph{Measure of uniqueness} {[}numeric{]} of individual analyses for the set of predictors in each model (\(uniq_i\)).
\item
  \emph{Measure of conservativeness} {[}numeric{]} of the model specification, as the number of random/group-level effects included (\(cons_i\)).
\item
  \emph{Number of post-hoc changes to the acoustic measurements} {[}numeric{]} the teams will report to have carried out (\(phoc_i\)).
\item
  \emph{Number of models} {[}numeric{]} the teams will report to have run (\(modn_i\)).
\item
  \emph{Major dimension} {[}categorical{]} that has been measured to answer the research question (\(mdim_i\)).
\item
  \emph{Temporal window} {[}categorical{]} that the measurement is taken over (\(twin_i\)).
\item
  \emph{Data exclusion}, {[}categorical{]} whether data has been excluded or not (\(excl_i\)).
\end{itemize}

The measure of uniqueness of predictors will be assessed by the Sørensen-Dice Index (SDI, Dice, 1945; Sørensen, 1948).
The SDI is an index typically used in ecology research to compare species composition across sites.
For our purposes, we will treat predictors as species and individual analyses as sites.
For each pair of analyses \((X, Y)\), the SDI will be obtained using the following formula:

@@

where \(|X \cap Y|\) is the number of variables common to both models in the pair, and \(|X|+|Y|\) is the sum of the number of variables that occur in each model.

In order to generate a unique SDI for each analysis team, we will calculate the average of all pairwise SDIs for all pairs of analyses using the \texttt{beta.pair()} function in the betapart R package (Baselga et al., 2020).

The major measurement dimension of each analysis will be categorized according to the following possible groups: \emph{duration}, \emph{amplitude}, \emph{fundamental frequency}, \emph{other spectral properties} (e.g.~frequency center of gravity, harmonics difference, etc.), \emph{other measures} (e.g.~principal components, vowel dispersion, etc.)
The temporal window that the measurement is taken over is defined by the target linguistic unit.
We assume the following relevant linguistic units: \emph{segment}, \emph{syllable}, \emph{word}, \emph{phrase}.

\textbf{Demographic factors}. We will include the following demographic factors about the teams:

\begin{itemize}
\tightlist
\item
  \emph{Research experience} {[}numeric{]} as the elapsed time from PhD award. Negative values will indicate that the person is a student or graduate studens (\(rexp_i\)).
\item
  \emph{Initial belief} {[}numeric{]} in the presence of an effect of atypical noun-adjective pairs on acoustics, as answered during the intake questionnaire (\(belf_i\)).
\end{itemize}

@@

\leavevmode\hypertarget{ref-baselga2020}{}%
Baselga, A., Orme, D., Villeger, S., De Bortoli, J., Leprieur, F., \& Logez, M. (2020). {b}etapart: Partitioning beta diversity into turnover and nestedness components. Retrieved from \url{https://CRAN.R-project.org/package=betapart}

@@

\leavevmode\hypertarget{ref-brugger2001}{}%
Brugger, P. (2001). From haunted brain to haunted science: A cognitive neuroscience view of paranormal and pseudoscientific thought. \emph{Hauntings and Poltergeists: Multidisciplinary Perspectives}, 195--213.

\leavevmode\hypertarget{ref-burkner2017}{}%
Bürkner, P.-C. (2017). {brms}: An {R} package for {Bayesian} multilevel models using {Stan}. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28. \url{https://doi.org/10.18637/jss.v080.i01}

@@

\leavevmode\hypertarget{ref-R-base}{}%
R Core Team. (2020). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}

@@

\leavevmode\hypertarget{ref-stan2020a}{}%
Stan Development Team. (2020). {RStan}: The {R} interface to {Stan}. Retrieved from \url{http://mc-stan.org/}

\leavevmode\hypertarget{ref-stan2021}{}%
Stan Development Team. (2021). Stan modeling language users guide and reference manual, v2.26.0. Retrieved from \url{http://mc-stan.org/}

@@

\leavevmode\hypertarget{ref-heuven2002}{}%
Van Heuven, V. J., Haan, J., Gussenhoven, C., \& Warner, N. (2002). Temporal distribution of interrogativity markers in {D}utch: A perceptual study. In \emph{Laboratory phonology 7} (Vol. 4, p. 61). Walter de Gruyter.
